ASP20 Boost

### 2020-08-15 Reports/report_2/2_REPORT.Rmd
- Fixed spelling errors across various documents. - New folder for term paper.

---
title: "ASP20 Boost"
author:
- Johannes Strauß
- Levin Wiebelt
- Sebastian Aristizabal
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: no
    latex_engine: xelatex
    template: null
    toc: yes
    toc_depth: 2
documentclass: report
geometry: left=4cm, right=3cm, top=2.5cm, bottom=2.5cm
lof: FALSE
lot: FALSE
bibliography:
- citavi.bib
- packages.bib
subtitle: Second Report
biblio-style: apalike
---

@@

```
model$beta
[1]  0.15122097  1.72916260  0.61363927 -0.14620695  0.02756381  0.28560006
> model$gamma
[1]  0.95706770  1.15196564 -0.02756374  0.00000000 -0.06839582  0.00000000
```
```
model$beta
[1]  0.15122097  1.72916260  0.61363927 -0.14620695  0.02756381  0.28560006
model$gamma
[1]  0.95706770  1.15196564 -0.02756374  0.00000000 -0.06839582  0.00000000
```
### Example Case

>>>>

---
title: "ASP20 Boost"
author:
- Johannes Strauß
- Levin Wiebelt
- Sebastian Aristizabal
date: 24.07.2020
output:
  pdf_document:
    keep_tex: no
    latex_engine: xelatex
    template: null
    toc: yes
    toc_depth: 2
documentclass: report
geometry: left=4cm, right=3cm, top=2.5cm, bottom=2.5cm
lof: FALSE
lot: FALSE
bibliography:
- citavi.bib
- packages.bib
subtitle: Second Report
biblio-style: apalike
---

@@

```
model$beta
[1]  0.15122097  1.72916260  0.61363927 -0.14620695  0.02756381  0.28560006
model$gamma
[1]  0.95706770  1.15196564 -0.02756374  0.00000000 -0.06839582  0.00000000
```
### Example Case
